---
title: "Scales Package"
format:
  html:
    self-contained: true
  pdf:
    latex-engine: xelatex
    keep-tex: true
editor: source
execute: 
  warning: false
  message: false
---


## TRYING TO RENDER PDF: /c/Users/Robert/AppData/Local/Programs/MiKTeX/miktex/bin/x64

## [PDF???](https://www.youtube.com/watch?v=t30sqFch2v0)
typist tl;dw  


 
## R Styled tables using tidyverse, gt and the scales packages

*ABBV* = Abbvie Inc., *BTC* = Bitcoin, *ETH* = Etherium

\[Torbjorn Storli0(https://www.youtube.com/watch?v=JCVlI4si46o&t=203s) suggests checking out {*XTS*} package that works with {zoo} package. These packages are included with {*quantmod*}

How-to [Quarto setup chunks](https://rstudio-conf-2022.github.io/get-started-quarto/materials/03-computation-editors.html#/knitropts_chunk-defaults)

```{r setup}

knitr::opts_chunk$set()

library(quantmod)
library(tidyverse)
library(gt)
library(scales)

startdate = as.Date("2014-01-01")
enddate = as.Date("2024-04-09")

 # get daily stock prices for Abbvie inc.
getSymbols("ABBV", from = startdate, to=enddate)
```

Convert Daily stock prices to monthly stock prices

```{r}

monthly_prices <- to.period(ABBV, period = 'months', OHLC = FALSE)

head(monthly_prices)
tail(monthly_prices) 
```

Convert data to a tibble; and date index to its own column:

```{r}

ABBV_data <- as_tibble(monthly_prices) |>
  mutate(Date = index(monthly_prices))
```

Clean up the ABBV tibble table

```{r}

ABBV_tibble = ABBV_data |>
  rename(Open = ABBV.Open,
        High = ABBV.High,
        Low = ABBV.Low,
        Close = ABBV.Close,
        Volume = ABBV.Volume,
        Adjusted = ABBV.Adjusted) |>

dplyr::select(Date, Open, High, Low, Close, Volume, Adjusted)
```

Create a gt table

```{r eval=TRUE}

ABBV_gt <- gt(ABBV_tibble) 

ABBV_tab <- ABBV_gt |>
 tab_header(
  
    title = md("**<font color = blue>Abbvie Inc, Monthly Stock Prices</font>**"),
    subtitle = md("**From** 2014 **to** 2024-04-09")
 ) |> 
 cols_width(c(Date:Adjusted)  ~ px(120)
  )

ABBV_tab
```
